Verifying Demonstrations

### 2018-02-28 paper/analysis.tex
Eve to Grace, Rusuk to Mallory

We note that Alice and Bob do not trust each other, for all they know one or the 
other could be an agent of Eve the autocrat.
\begin{itemize}
  \item Eve the evil autocrat,
  \item Rusuk the foreign nation state, and finally
\end{itemize}

@@

We consider two ways of reusing participation proofs:
\begin{enumerate}
  \item Alice and Bob can reuse old proofs by modifying the identifiers.
  \item Eve can reuse proofs by creating a manifesto which yields the same 
    identifier as Alice's protest, then try to create new nodes in the 
    \ac{tposet} that matches the ones used in the old proofs.
\end{enumerate}
We will now estimate the difficulty of both types of attacks.

@@

Eve (possibly with Rusuk's aid) wants to arrange a counter-protest.
One way to get a higher participation count is to use the same identifier as 
Alice's protest.
Since the identifier for the protest is the hash value of the manifest, Eve 
must find a second preimage for the hash function.

@@

Alice wants to arrange another protest against Eve.
Her manifesto can remain the same, thus the protest identifier remains the 
same.
She wants to reuse some old proofs.
The head value that are included in the proofs extend them too far back into 
time.
The digital signatures prevents her from changing them.
So an alternative is to create nodes in the \ac{tposet} which has the same 
hashes.

@@

Eve and Rusuk has an incentive to lower the confidence in the result.
One way they can do this is to say that the result does not contain all 
participation proofs.
Statements such as this should be proved: provide a valid but missing proof.

>>>>

We note that Alice and Bob do not trust each other, for all they know one or the 
other could be an agent of Grace the autocrat.
\begin{itemize}
  \item Grace the evil autocrat,
  \item Mallory the foreign nation state, and finally
\end{itemize}

@@

We consider two ways of reusing participation proofs:
\begin{enumerate}
  \item Alice and Bob can reuse old proofs by modifying the identifiers.
  \item Grace can reuse proofs by creating a manifesto which yields the same 
    identifier as Alice's protest, then try to create new nodes in the 
    \ac{tposet} that matches the ones used in the old proofs.
\end{enumerate}
We will now estimate the difficulty of both types of attacks.

@@

Grace (possibly with Mallory's aid) wants to arrange a counter-protest.
One way to get a higher participation count is to use the same identifier as 
Alice's protest.
Since the identifier for the protest is the hash value of the manifest, Grace 
must find a second preimage for the hash function.

@@

Alice wants to arrange another protest against Grace.
Her manifesto can remain the same, thus the protest identifier remains the 
same.
She wants to reuse some old proofs.
The head value that are included in the proofs extend them too far back into 
time.
The digital signatures prevents her from changing them.
So an alternative is to create nodes in the \ac{tposet} which has the same 
hashes.

@@

Grace and Mallory have an incentive to lower the confidence in the result.
One way they can do this is to say that the result does not contain all 
participation proofs.
Statements such as this should be proved: provide a valid but missing proof.

### 2018-02-28 paper/properties.tex
Eve to Grace, Rusuk to Mallory

We have three \emph{malicious} adversaries: Alice, Eve and Rusuk.
Alice the activist (and all the protesters) try to increase the count.
Eve the totalitarian dictator tries to decrease the count.
Additionally, Eve tries to deanonymize the participants to arrest them or 
\emph{convince} them to change their minds.
Finally, we have Rusuk who is represents another nation state.
Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
gain, thus supporting either Eve or Alice as he see fits.
Rusuk will thus also try to either increase or decrease the count.
We will now formally define some security properties specifying the 
computational effort needed by the adversaries to succeed.
We categorize the desired properties into verifiability and privacy.

@@

\begin{requirements}[V]
  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that it 
    has not been counted before.
    \begin{requirements}
    \item Temporal egligibility:%
      \label{CreatedAfterStart} prove that the data was created after the start of 
      the event;%
      \label{CreatedBeforeEnd} prove that the data was created before the end of 
      the event.
    \item Spatial eligibility:%
      \label{SpatiallyRelated} prove that the data is spatially related to the 
      physical location of the event.
    \item One-proof-per-person:%
      \label{CountOnce} prove that no individual can be counted more than once.
    \item Designated event:%
      \label{DesignatedEvent} prove that the data is designated for the event.
    \end{requirements}

@@

In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
\eg Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

>>>>

We have three \emph{malicious} adversaries: Alice, Grace and Mallory.
Alice the activist (and all the protesters) try to increase the count.
Grace the totalitarian dictator tries to decrease the count.
Additionally, Grace tries to deanonymize the participants to arrest them or 
\emph{convince} them to change their minds.
Finally, we have Mallory who is represents another nation state.
Mallory has some interest in affecting the state of Grace's regime, for Mallory's own 
gain, thus supporting either Grace or Alice as he see fits.
Mallory will thus also try to either increase or decrease the count.
We will now formally define some security properties specifying the 
computational effort needed by the adversaries to succeed.
We categorize the desired properties into verifiability and privacy.

@@

\begin{requirements}[V]
  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that it 
    has not been counted before.
    \begin{requirements}
    \item Temporal egligibility:%
      \label{CreatedAfterStart} prove that the data was created after the start of 
      the event;%
      \label{CreatedBeforeEnd} prove that the data was created before the end of 
      the event.
    \item Spatial eligibility:%
      \label{SpatiallyRelated} prove that the data is spatially related to the 
      physical location of the event.
    \item One-proof-per-person:%
      \label{CountOnce} prove that no individual can be counted more than once.
    \item Designated event:%
      \label{DesignatedGracent} prove that the data is designated for the event.
    \end{requirements}

@@

In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
\eg Grace can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.
